---
title: "Schedule"
output: html_document
---
```{r, echo=FALSE, message=FALSE, warning=FALSE}
library(tidyverse); library(kableExtra);library(stringr); library(pander)
library(lubridate)
options(knitr.table.format = "html", knitr.kable.NA = '') 
knitr::opts_chunk$set(echo=FALSE, message=FALSE, warning=FALSE) 
```

# Last Updated: `r format(Sys.time(), "%a %b %d %X")` {.tabset .tabset-fade .tabset-pills}

<p>
Unless specified otherwise, all assignments are due at midnight on the due date listed. The weekly quizzes are on material from the prior week. 
</p>
```{r}
# Read in schedule
wk_schedule <- read_csv("weekly_schedule.csv")

# Set semester start date and format weeks nicely
start.date <- as_date("2020/01/08")
no_wks <- 16
class_seq <- c(seq(no_wks)*7,seq(no_wks)*7+5) %>% sort
class_date <- start.date+class_seq-7
wk_schedule <- wk_schedule %>% dplyr::select(-Order) %>% 
  mutate(Date = paste(month(class_date[-length(class_date)]),
                      day(class_date[-length(class_date)]),sep="/"),
         Day = wday(class_date[-length(class_date)],label=T)) %>%
  transmute(Week = wknum, Day = Day, Date = Date, Topic = topic)
wk_schedule %>%
  kable(align="lccclc", escape=FALSE) %>%
  kable_styling(bootstrap_options = c("hover", "striped", 
                                      "responsive", "bordered")) %>%
  column_spec(1, bold = T) %>%
  collapse_rows(columns = 1, valign = "top") %>%
  row_spec(0,bold = T, color = "white", background = "#000000") %>%
  row_spec(c(4,14,18,19,24), bold = T,italic = T)


#