---
title: "GEOG 215: Lab 3"
subtitle: "Taming Mighty Census with TidyCensus"
author: "YOUR NAME"
output: 
  html_document:
    number_sections: true
    code_folding: hide
    toc: true
    toc_float:
      collapsed: TRUE
      smooth_scroll: TRUE

---

******


```{r check_packages, include = FALSE}
  # This code will install required packages if they are not already installed
  # ALWAYS INSTALL YOUR PACKAGES LIKE THIS!
  packageList <- c("tidycensus","sf","janitor")
  for(p in packageList){
    if (!requireNamespace(p)) {
      install.packages(p)
    }
  }
```


# Preparations

## Load required Packages

```{r load_packages}
##This is a named chunk called load_packages
library(tidyverse)
library(sf)
library(janitor)
library(tidycensus)
```

## Obtain and set Api Key
```{r}
# this is an unnamed code chunk. Both are fine. Named chunks are easier to debug.
## Type your api command here
#Similarly you need to create your own rcode chunks wherever you need to write code
```



# Analysis


## Get List of variables



## Import Census Data from tidycensus api based on list of variables



## Tame Data

### Remove Unnecessary Columns

### Clean Variable Names

### Creating new variables of interest

### Rearrange columns




## Tidy Your Data






## Transform Data





## Data Visualization Part 1



### Histograms (Plotting 1 continuous variable)


### Boxplots (Plotting 1 continuous 1 categorical variable)

### Point plot




##  Data Viz Part 2: Adding Spatial Data

### Downloading and Importing Spatial Data

### Join your data

### Plot maps





# Feedback

