---
title: "Data Types and Formats in R"
author: 
- GEOG215, Introduction to Spatial Data Science \newline
- Varun Goel
date: '`r format(Sys.Date(), "%B %d, %Y")`'
output: 
  html_document:
    mathjax: null
---

```{r setup, include=FALSE, eval = F, echo=T}
knitr::opts_chunk$set(echo = TRUE, eval = F)
```

## Data Types in R {.tabset}

### Character

**A character object is used to store string values in R.  Note that anthing with a character value is inside quotations when displayed in R.**

<details>
  <summary>Create and get information about character object 1</summary>
```{r echo = TRUE, eval = F}
# Create an object with a single character value
char <- "character data"
# Print object to console
char
# Get type of object
typeof(char)
# Get class of object
class(char)
# Get structure of object
str(char)
# Ask if object is character
is.character(char)
# Number of characters?
nchar(char)
```
</details>

<details>
  <summary>Subsetting within character object</summary>
```{r echo = TRUE, eval = F}
# Create an object with a single character value
char <- "character data"
char
# Get first five characters
substr(char, 1, 5)
# Get last seven characters
substr(char, nchar(char)-7, nchar(char))
```
</details>

<details>
  <summary>Create and get information about character object 2</summary>
```{r echo = TRUE, eval = F}
# Create an object with multiple character values
char <- c("a", "GEO", "course")
# Print object to console
char
# Get type of object
typeof(char)
# Get class of object
class(char)
# Get structure of object
str(char)
# Ask if object is character
is.character(char)
# Number of characters?
nchar(char)
```
</details>

<details>
  <summary>Convert to character object</summary>
```{r echo = TRUE, eval = F}
# Convert object to character
as.character(1)
# Convert multiple objects to character
as.character(1:10)
```
</details>

<br>

### Numeric

**A numeric object is used to store numbers in R.**

<details>
  <summary>Create and get information about numeric object 1</summary>
```{r echo = TRUE, eval = F}
# Create an object with a single numeric value
num <- 1.0
# Print object to console
num
# Get type of object
typeof(num)
# Get class of object
class(num)
# Get structure of object
str(num)
# Ask if object is character
is.character(num)
# Ask if object is numeric
is.numeric(num)
```
</details>

<details>
  <summary>Create and get information about numeric object 2</summary>
```{r echo = TRUE, eval = F}
# Create an object with a multiple numeric values
num <- 1:10
# Print object to console
num
# Get type of object
typeof(num)
# Get class of object
class(num)
# Get structure of object
str(num)
# Ask if object is numeric
is.numeric(num)
```
</details>

<details>
  <summary>Convert to numeric object</summary>
```{r echo = TRUE, eval = F}
# Convert object to numeric
as.numeric("1")
# Convert multiple objects to numeric
as.numeric(c("1", "2", "2"))
# Convert multiple objects to numeric
as.numeric(c("1", "100", "blue"))
```
</details>

<br>

### Logical

**A logical object is used to store TRUE / FALSE (or 1 / 0) values in R. These result from logical queries.**

<details>
  <summary>Create and get information about logical object</summary>
```{r echo = TRUE, eval = F}
# Create an object with a single logical value
lo <- TRUE
# Print object to console
lo
# Get type of object
typeof(lo)
# Get class of object
class(lo)
# Get structure of object
str(lo)
# Ask if object is character
is.character(lo)
# Ask if object is numeric
is.numeric(lo)
# Ask if object is logical
is.logical(lo)
```
</details>

<details>
  <summary>Logical objects and results of queries</summary>
```{r echo = TRUE, eval = F}
# Example queries
3 > 2
2 > 3
1 %in% 1:20
1 %in% 10:20
1:20 %in% 5
```
</details>

<details>
  <summary>Convert to  logical object</summary>
```{r echo = TRUE, eval = F}
# Convert object to logical
as.logical("1")
# Convert object to logical
as.logical(1)
# Convert object to logical
as.logical(0)
# Convert object to logical
as.logical(2)
# Convert object to logical
as.logical(c(1,0,0,1,0))
```
</details>

<details>
  <summary>Logical object as numeric</summary>
```{r echo = TRUE, eval = F}
# Convert object to logical
lo <- as.logical(c(1,0,0,1,0))
# Use sum function to find how many "TRUE"s
sum(lo)
```
</details>

## Data Structures in R {.tabset}

### Vector

**Vector is a basic data structure in R. It contains elements of the same type.**

<details>
  <summary>Create vectors</summary>
```{r echo = TRUE, eval = F}
# Numeric
a.numeric.vector <- 1:10
a.numeric.vector
# Numeric
a.numeric.vector <- 100:80
a.numeric.vector
# Numeric sequence
a.numeric.vector <- seq(0, 20, 2)
a.numeric.vector
# Repeating value
a.numeric.vector <- rep(2.5, 5)
a.numeric.vector
# Character
a.char.vector <- c("A", "a", "aye?")
a.char.vector
# Mix elements of different types
a.vector <- c("A", TRUE, 1)
a.vector
# Append two vectors
a.vector <- 1:10
b.vector <- 100:110
c.vector <- c(a.vector, b.vector)
c.vector
```
</details>


<details>
  <summary>Get info about vector</summary>
```{r echo = TRUE, eval = F}
# Create numeric vector
a.numeric.vector <- 100:110
a.numeric.vector
# How many elements?
length(a.numeric.vector)
# Max, min, mean
max(a.numeric.vector)
min(a.numeric.vector)
mean(a.numeric.vector)
```
</details>

<details>
  <summary>Vector subsetting</summary>
```{r echo = TRUE, eval = F}
# Create numeric vector
a.numeric.vector <- 100:110
# 5th element
a.numeric.vector[5]
# 2nd to 8th element
a.numeric.vector[2:8]
# Which element of vector equal to value
which(a.numeric.vector == 102)
a.numeric.vector[3]
# Which element(s) of vector less than value
which(a.numeric.vector < 103)
a.numeric.vector[1:3]
```
</details>

### Factor

**A factor object stores nominal values as a vector of integers in the range [1-k] (where k is the number of unique values in the nominal variable), and an internal vector of character strings (the original values) mapped to these integers.**

**These can be both very useful and very confusing when used in data frames in R!**

<details>
  <summary>Working with factors</summary>
```{r echo = TRUE, eval = F}
# Create factor
fac <- factor(c("a", "b", "b", "a"))
fac
# Get information about factor
class(fac)
levels(fac)
length(fac)
# Be careful! You can't use values that are not in the levels
fac[2] <- "c"
fac
# Watch out for conversion!
as.numeric(fac)
as.character(fac)
# If your data are not clean, 
# R will read in a numeric variable as a factor
ex.dat <- data.frame(ID = 1:10, VALUE = c(101:109, "-"))
str(ex.dat)
ex.dat
# Note what happens on convert to numeric
ex.dat$VALUECONVERT <- as.numeric(ex.dat$VALUE)
ex.dat
# That's no good, try this
ex.dat$VALUECONVERT2 <- as.numeric(as.character(ex.dat$VALUE))
ex.dat

```
### Matrix

**A matrix is an extension of the vector data structure. A matrix is simply an atomic vector with two dimensions: rows and columns. A matrix is similar to a table, but without the "awareness" that it is a a table.**

<details>
  <summary>Create matrices</summary>
```{r echo = TRUE, eval = F}
# Create empty
m <- matrix(nrow = 2, ncol = 2)
m
# Create, populate by column
m <- matrix(c(1, 2, 3, 4, 5, 6), nrow = 2, ncol = 3)
m
# Create, populate by row
m2 <- matrix(c(1, 2, 3, 4, 5, 6), nrow = 2, ncol = 3, byrow = TRUE)
m2
# Create by appending as columns
first.vec <- 1:5
second.vec <- 6:10
m3 <- cbind(first.vec, second.vec)
m3
# Create by appending as rows
first.vec <- 1:5
second.vec <- 6:10
m3 <- rbind(first.vec, second.vec)
m3
```
</details>

<details>
  <summary>Get info about matrix</summary>
```{r echo = TRUE, eval = F}
# Create, populate by row
m2 <- matrix(c(1, 2, 3, 4, 5, 6), nrow = 2, ncol = 3, byrow = TRUE)
m2
# Type
class(m2)
# Dimensions
dim(m2)
# Number of elements (total)
length(m2)
```
</details>

<details>
  <summary>Matrix subsetting</summary>
```{r echo = TRUE, eval = F}
# Create, populate by row
m2 <- matrix(c(1, 2, 3, 4, 5, 6), nrow = 2, ncol = 3, byrow = TRUE)
m2
# 2nd row
m2[2,]
# 2nd column
m2[,2]
# 1st and 2nd column
m2[,1:2]
# By element (not recommended)
m2[4]
```
</details>

### Array

**COMING SOON**

### Data Frame

**A data frame is a two dimensional object. It is similar to a matrix, but different columns can contain different modes of data (numeric, character, logical, and so on). A data frame is similar to the datasets in SAS, SPSS, and Stata. Data frames are the most common data structure you will be dealing with in R.**

<details>
  <summary>Create data frame and get information</summary>
```{r echo = TRUE, eval = F}
# Create from set of vectors with same length
patientID <- c(1, 2, 3, 4, 5)
age <- c(25, 34, 28, 52, 35)
diabetes <- c("Type1", "Type2", "Type1", "Type1", "Type2")
status <- c("Poor", "Improved", "Excellent", "Poor", "Poor")
patientdata <- data.frame(patientID, age, diabetes, status)
patientdata
# Type
class(patientdata)
# Dimensions, number of rows, number of columns
dim(patientdata)
nrow(patientdata)
ncol(patientdata)
# Data types for each column
str(patientdata)
```
</details>

<details>
  <summary>Data frame subsetting</summary>
```{r echo = TRUE, eval = F}
# See content above for patientdata object creation
# 2nd row
patientdata[2,]
# 2nd column
patientdata[,2]
# 1st and 2nd column
patientdata[,1:2]
# By column name
patientdata$patientID
```
</details>


### List

**A list acts as a container. The contents of a list are not restricted to a single mode and can encompass any mixture of data types. Lists are sometimes called generic vectors, because the elements of a list can by of any type of R object, even lists containing further lists. A list is somewhat similar to a data frame, but the contents of each vector do not have to be the same length**

<details>
  <summary>Create list and get information</summary>
```{r echo = TRUE, eval = F}
# Create list from multiple vectors and objects
numbers <- 1:5
characters <- c("a", "b", "c")
lo <- TRUE
ex.list <- list(numbers, characters, lo)
ex.list
# What kind of object?
class(ex.list)
# Data types for each element
str(ex.list)
# Number of list elements
length(ex.list)
# Name list elements
names(ex.list) <- c("numbers", "characters", "logical")
ex.list
names(ex.list)
```
</details>


<details>
  <summary>List subsetting</summary>
```{r echo = TRUE, eval = F}
# See content above for ex.list object creation
# 2nd element of list
ex.list[[2]]
# 2nd element of list, by name
ex.list$characters
# 3rd element of 2nd element of list
ex.list[[2]][3]
# 3rd element of 2nd element of list
ex.list$characters[3]
```
</details>
