---
title: "Point Pattern Analysis"
subtitle: Geog 215
author: Varun Goel
output: 
  html_document:
    theme: cosmo
---

```{r setup, include=TRUE,  results = 'hide', warning=FALSE, message = FALSE}
knitr::opts_chunk$set(echo = TRUE, warning=FALSE, message = FALSE)
library(tidyverse)
library(sf)
library(tmap)
library(tmaptools)
library(spatstat) # for point pattern analysis
library(maptools) # for point pattern analysis
library(raster)
library(aspace) # for centrography
```

# Load data

```{r, message=F, warning=FALSE, results='hide'}
cholera <- st_read("data/SnowGIS/Cholera_Deaths.shp")
pumps <- st_read("data/SnowGIS/Pumps.shp")
```

# create bbox for cholera and add buffer

```{r}

london <- st_as_sfc(st_bbox(cholera) + c(-50, -50, 50, 50))
st_crs(london) <- st_crs(cholera)
```

## John Snow's redefined map

```{r}
tmap_mode("view")
tm_basemap("Stamen.Toner") + tm_shape(cholera) + tm_dots(col = "red") +
  tm_shape(pumps) + tm_dots(col ="green") +
  tm_tiles("Stamen.TonerLabels")
```

## Basic version of map with London Boundary

```{r}
tmap_mode("plot")
  tm_shape(london) + tm_borders(col = "black") +
tm_shape(cholera) + tm_dots(col = "red", size = 1, alpha = 0.4) +
  tm_shape(pumps) + tm_dots(col ="green", size = 1)
```

# Set up data for point pattern analysis

We convert our `sf` objects to a format that are required for the `spatstat` package. In addition we set our points as "unmarked" which means that we do not care about any attributes/values attached to each point. If we care about the attributes, those points are considered "marked".

```{r}
cholera.sp <- as(cholera, "Spatial")
cholera.ppp <- as(cholera.sp, "ppp")

pumps.sp <- as(pumps, "Spatial")
pumps.ppp <- as(pumps.sp, "ppp")
# Dont use Marked points
marks(cholera.ppp)  <- NULL
marks(pumps.ppp)  <- NULL
# set observation window
city.sp <- as(london, "Spatial")
city.owin <- as.owin(city.sp)
Window(cholera.ppp) <- city.owin
```

# Quadrat analysis

```{r}
#6 by 6 window
qcounts1<-quadratcount(cholera.ppp, nx = 6, ny = 6)
```

# 6 by 6 Quadrat

```{r}

plot(cholera.ppp, pch=20, cols="grey70", main=NULL)
#The plot the cells and counts 
plot(qcounts1, col = "red", add=TRUE)
```

```{r}
# performing a VMR test

Qcount<-data.frame(qcounts1)
var(Qcount$Freq)/mean(Qcount$Freq)
quadrat.test(cholera.ppp, nx = 6, ny = 6)
```
## Map quadrat density

```{r}
qcounts1.d <- intensity(qcounts1)
# Plot the density
plot(intensity(qcounts1, image=TRUE), main=NULL, las=1)  # Plot density raster
plot(cholera.ppp, pch=20, cex=0.6, col=rgb(0,0,0,.5), add=TRUE)  # Add points
plot(pumps.ppp, pch=20, cex=2, col="red", add=TRUE)
```

# quadrat 20 by 20

```{r}
qcounts2<-quadratcount(cholera.ppp, nx = 20, ny = 20)
plot(cholera.ppp, pch=20, cols="grey70", main=NULL)
#The plot the cells and counts 
plot(qcounts2, col = "red", add=TRUE, cex = 0.6)
```



```{r}
Qcount<-data.frame(qcounts2)
var(Qcount$Freq)/mean(Qcount$Freq)
quadrat.test(cholera.ppp, nx = 20, ny = 20)
```

```{r}
qcounts2.d <- intensity(qcounts2)
# Plot the density
plot(intensity(qcounts2, image=TRUE), main=NULL, las=1)  # Plot density raster
plot(cholera.ppp, pch=20, cex=0.6, col=rgb(0,0,0,.5), add=TRUE)  # Add points
plot(pumps.ppp, pch=20, cex=2, col="red", add=TRUE)
```



# Kernel Density estimation

## Using default kernal window
```{r}
K1 <- density(cholera.ppp) # Using the default bandwidth
plot(K1, main=NULL, las=1)
contour(K1, add=TRUE)
```
# using same gaussian window but half the bandwith

```{r}
K2 <- density(cholera.ppp, adjust = 0.5) # Using the default bandwidth
plot(K2, main=NULL, las=1)
contour(K2, add=TRUE)
```
## specify size of bandwidth

```{r}
K3 <- density(cholera.ppp, sigma = 20) # Using the default bandwidth
plot(K3, main=NULL, las=1)
contour(K3, add=TRUE)
```

## Weighted pattern by number of household members who died

```{r}
wppp <- ppp(st_coordinates(cholera)[,1], st_coordinates(cholera)[,2], window = city.owin, marks=NULL)
K4 <- density(wppp, sigma = 20, weights = cholera$Count/sum(cholera$Count)) # Using the default bandwidth
plot(K4, main=NULL, las=1)
contour(K4, add=TRUE)
```

## Plot using tmap
```{r}
kernel_r <- raster(K4)
projection(kernel_r) <- crs(cholera.sp)
```

```{r}
tmap_mode("plot")
tm_shape(kernel_r) + tm_raster(palette = "plasma") + 
  tm_shape(cholera) + tm_dots(col= "red", size = 0.05, alpha = 0.4,
                              border.col = "white", border.lwd = 2) +
  tm_shape(pumps) + tm_dots(col = "blue", size = 0.2, border.col = "white", border.lwd = 2)
 
```

# Nearest Neighbor

## Mean nearest neighbors

```{r}
cholera.nndist <- nndist(cholera.ppp)
mean(cholera.nndist)
```

## Significance test for clustering

```{r}
clarkevans.test(cholera.ppp)
```

```{r}
ANN <- apply(nndist(cholera.ppp, k=1:100),2,FUN=mean)
plot(ANN ~ eval(1:100), type="b", main=NULL, las=1)
```

