---
title: "Pick 2 Countries - comparing trends in population  over time"
output:
  word_document: default
  pdf_document: default
---

# Purpose

This document contains analysis for comparing population trends

## Required Libraries 
```{r}
knitr::opts_chunk$set(echo = TRUE)
# SET this to FALSE to only show results but no code in all parts of the document
if (!require("ggplot2")) install.packages("ggplot2")
library(ggplot2)

```

## Data

Always add as many details as possible about your data including where it came from, how it was processed, licensing, and where it can be accessed. 

- Gapminder data [available here](http://www.gapminder.org/data/). [Gapminder data is licensed CC-BY 3.0](https://docs.google.com/document/pub?id=1POd-pBMc5vDXAmxrpGjPLaCSDSWuxX6FLQgq5DhlUhM#h.ul2gu2-uwathz).

**Read in data**: To read in the data, make sure this file is in the same directory/folder as the `gapminderDataFiveYear.txv` file.  To set the proper working directory go to Session > Set Working Directory > To Source File Location. 

```{r}
## Read in Data
gapMinder <- read.delim("gapminderDataFiveYear.tsv") 

### Check data 
head(gapMinder) #First 10 lines of dataset
dim(gapMinder) #number of rows and columns in data set
```

You can see what countries are available by looking at the how many unique categories are in the country column of the gapMinder dataset.

```{r, results='hide'}
# results ='hid' does not show printed table
levels(gapMinder$country)
```

### Pick 2 Countries

Now pick 2 countries that you are intrested in.  Just replace with the countries name below.

```{r}
### Pick 2 Countries
countryName1 <- "United States" # Replace with your Country 1
countryName2 <- "China" # Replace with your Country 2
```

## Individual countries

### Country One

We want to look at how population changes over time for the first country.  

```{r echo =FALSE}
# Use echo = FALSE to prevent code but not results from showing up
country1 <- subset(gapMinder, country == countryName1)

ggplot(country1, aes(year, pop)) + 
  geom_path() +
  ggtitle(countryName1) +
  theme(plot.title = element_text(size = 15, face = "bold")) 
```

This second graph is looking at the correlation between life expectancy (lifeExp) and GDP per person (gdpPercap). The size of the circles on the plot represents total population.

```{r echo = TRUE}
ggplot(country1, aes(gdpPercap, lifeExp, size = pop)) + 
  geom_point() +
  ggtitle(countryName1) +
  theme(plot.title = element_text(size = 15, face = "bold"))
```

### Country Two

Add description for Country to here

```{r, echo=FALSE}
# add code for plotting population vs time
```

**Notes**: In a real report you can add information about the results of the analysis you are performing.  That way your code, analysis, questions, and results are all in one place. 

```{r, echo = FALSE}
# add code for plotting life expectancy vs gdp
```

## Both Countries Together

Add chunks for both countries together


## Conclusions

Add conclusions about your finding
